\chapter{List of Publications}

\lettrine[findent=2pt]{\textbf{B}}{}elow, the publications that have direct relation with this theses.

%This benchmark was created using the runtime StarPU. A set of applications were executed over CPUs and GPUs and all profile information was collected to created the SWFs and their respective dependencies or precedence relations. 

% \todo[inline]{Citar os paper HiPC, NCA, Europar}

\begin{itemize}
\bibitem[Amaris {\rm{\em et~al.}} (2015)Amaris, Cordeiro, Goldman, e
  Camargo]{amaris:2015:HiPC}
{\bf Marcos Amaris}, Daniel Cordeiro, Alfredo Goldman and Raphael~Y.de Camargo.
\newblock A simple bsp-based model to predict execution time in gpu
  applications.
\newblock In \emph{High Performance Computing (HiPC), 2015 IEEE 22nd
  International Conference on}, p\'{a}ginas 285--294.
  
\bibitem[Amaris {\rm{\em et~al.}} (2016)Amaris, de~Camargo, Dyab, Goldman, e
  Trystram]{Amaris:2016:NCA}
{\bf Marcos~Amaris}, Raphael~Y.de Camargo, Mohammed~Dyab, Alfredo~Goldman and Denis~Trystram.
\newblock A comparison of GPU execution time prediction using machine learning
  and analytical modeling.
\newblock In \emph{2016 IEEE 15th International Symposium on Network Computing
  and Applications (NCA)}, pages 326--333.

 \bibitem[Mommessin {\rm{\em et~al.}} (2017)Mommessin, Amaris, Lucarelli, e
  Trystram]{Mommessin:2017}
Clement~Mommessin, {\bf Marcos~Amaris}, Giorgio~Lucarelli and Denis~Trystram.
\newblock Generic algorithms for scheduling applications on hybrid multi-core
  machines.
\newblock In \emph{2017 Euro-Par: International Conference on Parallel and
  Distributed Computing}, pages 220--231.
  
  \bibitem[Mommessin {\rm{\em et~al.}} (2018)Mommessin, Amaris, Lucarelli, e
  Trystram]{mommesin:2017:CCPE}
Clement~Mommessin, {\bf Marcos~Amaris}, Giorgio~Lucarelli and Denis~Trystram.
\newblock Generic algorithms for scheduling applications on heterogeneous multi-core platforms
\newblock \emph{arXiv preprint arXiv:1711.06433} in revision. 
 
\end{itemize}

There are other works which were published during the Doctorate of the candidate, although they were not directly related to this theses, they were in the area of High Performance Computing and they were collaboration that the candidate did with other researchers, these are:
%\cite{bruel:2015:WSCAD}\cite{gonccalves:2016:HICSS}\cite{okada:2015:WSCAD}\cite{bruel:2017:CCPE}


\begin{itemize}
  \bibitem[Okada {\rm{\em et~al.}} (2015)Okada, Amar{\'\i}s, e vel
  Lejbman]{okada:2015:WSCAD} 
Thiago~Kenji Okada, {\bf Marcos Amar{\'\i}s} e Alfredo~Goldman vel Lejbman.
\newblock Scheduling moldable bsp tasks on clouds.
\newblock In \emph{WSCAD'15 - XVI Simp{\'o}sio em Sistemas Computacionais de
  Alto Desempenho},
    
    \bibitem[Bruel {\rm{\em et~al.}} (2015)Bruel, Amar{\'\i}s, e
  Goldman]{bruel:2015:WSCAD}
Pedro Bruel, {\bf Marcos Amar{\'\i}s} and Alfredo Goldman.
\newblock Autotuning gpu compiler parameters using opentuner.
\newblock In \emph{WSCAD'15 - XVI Simp{\'o}sio em Sistemas Computacionais de
  Alto Desempenho}, pages\'{a}ginas 13--23.
  
  
  \bibitem[Gon{\c{c}}alves {\rm{\em et~al.}} (2016)Gon{\c{c}}alves, Amar{\'\i}s,
  Okada, Bruel, e Goldman]{gonccalves:2016:HICSS}
Rog{\'e}rio Gon{\c{c}}alves, {\bf Marcos Amar{\'\i}s}, Thiago Okada, Pedro Bruel and
  Alfredo Goldman.
\newblock Openmp is not as easy as it appears.
\newblock In \emph{49th Hawaii International Conference on System Sciences}, January-2016,
  pages 5742--5751.

\bibitem[Bruel {\rm{\em et~al.}} (2017)Bruel, Amar{\'\i}s, e
  Goldman]{bruel:2017:CCPE}
Pedro Bruel, {\bf Marcos Amar{\'\i}s} and Alfredo Goldman.
\newblock Autotuning cuda compiler parameters for heterogeneous applications
  using the opentuner framework.
\newblock \emph{Concurrency and Computation: Practice and Experience}
    29\penalty0 (22). 2017


\end{itemize}  